---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Mix3Trees

<!-- badges: start -->
<!-- badges: end -->

This `R` package provides functions to estimate *3Tree* models, as described in the paper

Gottard, A., Vannucci, G., Grilli, L., & Rampichini, C. (2023). Mixed-effect models with trees. Advances in Data Analysis and Classification, 17(2), 431-461.


## Installation

To install the package, run 

``` r
install.packages("devtools")
devtools::install_github("agottard/Mix3Trees")
library(Mix3Trees)
```

## Example

This is a basic example which shows you how to use the main function:

```{r example}
library(Mix3Trees)
### You can use this simulated dataset to practice
data(mydat)

names(mydat)

X<-mydat[,1:5]
mod1 <- fit3Trees(Y=mydat$Y, X=X, gr=mydat$gr,
                  covLin=names(X), covT1=names(X[,1:3]),
                  covT2=names(X[,4:5]), covT3=colnames(X),
                  niter = 50, re_form = "(1|gr)",
                  selective.inference = FALSE)

summary(mod1$mod.final)
```

You can plot your tree component running this code

```{r pressure, echo = FALSE}
plot3T(mod1, tree = 1)
```


